---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggcheck

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ggcheck)](https://CRAN.R-project.org/package=ggcheck)
[![R-CMD-check](https://github.com/rstudio/ggcheck/workflows/R-CMD-check/badge.svg)](https://github.com/rstudio/ggcheck/actions)
<!-- [![](http://cranlogs.r-pkg.org/badges/last-month/ggcheck?color=blue)](https://cran.r-project.org/package=ggcheck) -->
<!-- badges: end -->

ggcheck provides functions that inspect [ggplot2] objects to make it easier for teachers to check that student plots meet expectations. Designed primarily for automated grading via [gradethis] in interactive [learnr] tutorials.

## Installation

You can install ggcheck from [GitHub][gh-ggcheck] with:

``` r
# install.packages("remotes")
remotes::install_github("rstudio/ggcheck")
```

## Usage

The primary goal of ggcheck is to help tutorial authors inspect and test properties of [ggplot2] plots.
The examples below demonstrate how ggcheck can be used in general;
for more information about using gradethis in learnr tutorials,
please see the [gradethis package documentation](https://pkgs.rstudio.com/gradethis/).

Suppose an exercise asks students to create the following plot
of engine displacement vs highway miles per gallon ratings.

```{r expected-plot}
library(ggplot2)

p <-
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color = class)) +
  geom_smooth(se = FALSE, method = "lm")

p
```

We can use ggcheck to test that students used `geom_point()`

```{r test-geom-point}
library(ggcheck)

uses_geoms(p, "point", exact = FALSE)
```

or that both `geom_point()` and `geom_smooth()` were used

```{r test-geom-both}
uses_geoms(p, c("point", "smooth"), exact = FALSE)
```

or that exactly both `geom_point()` and `geom_smooth()` were used and in that order.

```{r test-geom-both-exact}
uses_geoms(p, c("point", "smooth"), exact = TRUE)
```

Similarly, we can test that a linear model was used for the smoothing method
and the confidence interval was not displayed:

```{r test-geom-params}
uses_geom_param(p, "smooth", list(se = FALSE, method = "lm"))
```

There's a lot more that ggcheck can do.
Read more in the [full function listing](https://rstudio.github.io/ggcheck/).

[gh-ggcheck]: https://github.com/rstudio/ggcheck
[ggplot2]: https://ggplot2.tidyverse.org
[gradethis]: https://pkgs.rstudio.com/gradethis
[learnr]: https://rstudio.github.io/learnr/
