The primary goal of ggcheck is to help tutorial authors inspect and test properties of [ggplot2] plots.
The examples below demonstrate how ggcheck can be used in general;
for more information about using gradethis in learnr tutorials,
please see the [gradethis package documentation](https://pkgs.rstudio.com/gradethis/).

Suppose an exercise asks students to create the following plot
of engine displacement vs highway miles per gallon ratings.

```{r expected-plot}
library(ggplot2)

p <-
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color = class)) +
  geom_smooth(se = FALSE, method = "lm")

p
```

We can use ggcheck to test that students used `geom_point()`

```{r test-geom-point}
library(ggcheck)

uses_geoms(p, "point", exact = FALSE)
```

or that both `geom_point()` and `geom_smooth()` were used

```{r test-geom-both}
uses_geoms(p, c("point", "smooth"), exact = FALSE)
```

or that exactly both `geom_point()` and `geom_smooth()` were used and in that order.

```{r test-geom-both-exact}
uses_geoms(p, c("point", "smooth"), exact = TRUE)
```

Similarly, we can test that a linear model was used for the smoothing method
and the confidence interval was not displayed:

```{r test-geom-params}
uses_geom_param(p, "smooth", list(se = FALSE, method = "lm"))
```

There's a lot more that ggcheck can do.
Read more in the [full function listing](https://rstudio.github.io/ggcheck/).
